Compare pseqs

### 2019-05-31 comparepseqs.Rmd
Minor

```{r install, eval = FALSE, include = FALSE}
install.packages("BiocManager")
BiocManager::install("phyloseq")

source("https://bioconductor.org/biocLite.R")
biocLite("BiocInstaller")
library(BiocInstaller)
source("http://www.bioconductor.org/biocLite.R")
biocLite("microbiome")
```

@@

```{r models}
ret <- list()

@@

        if ("beta" %in% names(missing)) {
            message("Missing beta")
            betadiversity <- list(min = calculateadonis(dset = dset,
                                                        matrix = bray.dist.matrix,
                                                        covariates = covariates.min,
                                                        npermutations = 1000),
                                  full = calculateadonis(dset = dset,
                                                         matrix = bray.dist.matrix,
                                                         covariates = covariates.full,
                                                         npermutations = 1000))
            saveRDS(betadiversity, file = paste0("rds-comparepseqs/beta-", key , ".rds"))
        }
    }

@@

```{r plot alpha-beta}
if (!exists("subset.run")) {
    plotlist <- list()

@@

        ggsave(file = paste0("cache/alpha-beta-", key , ".png"), plot=g4, height=6, width=9)
        plotlist[[key]] = g4
    }

    g <- arrangeGrob(grobs = plotlist, ncol=2)
    ggsave(file="cache/plotlist.png", g, height=6*length(plotlist)/1.5, width=10*2)
} else {
    message("Skipping graphics")
}
```

@@

```{r debug alpha, eval = FALSE}
scatterplot.df <- lapply(ret, function(x) x$alphadistribution) %>%
    Reduce(function(x, y) merge(x, y, all=TRUE, by="Sample_ID"), .) %>%
    select(-Sample_ID) %>%
    na.omit()

scatterplot.df %>% head

 lapply(ret, function(x) x$alphadistribution %>% head)

ggsave(file = paste0("cache/ggpairs-alphas.png"),
       plot=ggpairs(scatterplot.df,
                        lower = list(continuous = wrap("points",
                                                       alpha = 0.3,
                                                       size=0.1), 
                                     combo = wrap("dot",
                                                  alpha = 0.4,
                                                  size=0.2))),
       height=6,
       width=9,
       unit = "in",
       dpi = 300)

>>>>

@@

```{r alpha scatter, include = FALSE, eval = FALSE}
rds = rds[c(1,2,4)]
ret <- list()

    ret[[key]] = list("alphadistribution" = alphadistribution)
}
```

```{R models}
ret <- list()

@@

        if ("beta" %in% names(missing)) {
            message("Missing beta")
            betadiversity <- list(min = calculateadonis(dset = dset,
                                                        matrix = bray.dist.matrix,
                                                        covariates = covariates.min,
                                                        npermutations = 100),
                                  full = calculateadonis(dset = dset,
                                                         matrix = bray.dist.matrix,
                                                         covariates = covariates.full,
                                                         npermutations = 100))
            saveRDS(betadiversity, file = paste0("rds-comparepseqs/beta-", key , ".rds"))
        }
    }

@@

```{r plot alpha-beta}
names(rds)
if (!exists("subset.run")) {
    plotlist <- list()

@@

        ggsave(file = paste0("cache/alpha-beta-", key , ".png"), plot=g4, height=6, width=9)

        plotlist[[key]] = g4
    }

    g <- arrangeGrob(grobs = plotlist, ncol=2)
    ggsave(file="cache/plotlist.png", g, height=6*length(plotlist)/1.5, width=10*2)

} else {
    message("Skipping graphics")
}
```

@@

# Alpha scatter

```{r draw alpha distribution scatter plot, eval = FALSE}
scatterplot.df <- lapply(ret, function(x) x$alphadistribution) %>%
    Reduce(function(x, y) merge(x, y, all=TRUE, by="Sample_ID"), .) %>%
    select(-Sample_ID) %>%
    na.omit()

galphascatter <- ggpairs(scatterplot.df,
                         lower = list(continuous = wrap("points",
                                                        alpha = 0.3,
                                                        size=0.1), 
                                      combo = wrap("dot",
                                                   alpha = 0.4,
                                                   size=0.2))) +
    theme(legend.position = "none", 
          panel.grid.major = element_blank(), 
          axis.ticks = element_blank(), 
          panel.border = element_rect(linetype = "dashed", colour = "black", fill = NA))

ggsave(file = paste0("cache/ggpairs-alphas.png"),
       plot= galphascatter,
       height=6,
       width=9,
       unit = "in",
       dpi = 300)
